%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

%---------------------------------------------------------
\begin{cvparagraph}
\begin{enumerate}[label={[\arabic*]}]
		\item {\href{https://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0006846} {Chowdhury R, Chowdhury V, Faria S, Islam S, Maheswary NP, Akhter S, \textbf{Islam MS}, Dash AP, Kroeger A, Banu Q.  \textbf{\textit{Indoor residual spraying for kala-azar vector control in Bangladesh: A continuing challenge.}} PLoS neglected tropical diseases. 2018 Oct 1;12(10):e0006846.}}	

		\item {\href{http://www.eurekaselect.com/node/161266/article/mining-gene-expression-profile-with-missing-values-an-integration-of-kernel-pca-and-robust-singular-values-decomposition} {Islam MS, Hoque MA, \textbf{Islam MS}, Ali M, Hossen B, Binyamin M, Merican AF, Akazawa , Kumar N, Sugimoto M. \textbf{\textit{"Mining Gene Expression Profile with Missing Values: An integrated implementation of Kernel PCA and Singular Value Decomposition"}}. Current Bioinformatics, 13(2018):1-12, issn 1574-8936/2212-392X, doi 10.2174/157489361366618041315165413(2)}}

		\item {\href{https://dl.acm.org/citation.cfm?id=2982182} {Hahn T, Rahman HU, Segall R, Heim C, Brunson R, Sharma A, Aslam M, Lara-Rodriguez A, \textbf{Islam MS}, Gupta N, Embry CS. \textbf{\textit{"Remote access programs to better integrate individuals with disabilities."}} In Proceedings of the 18th International ACM SIGACCESS Conference on Computers and Accessibility 2016 Oct 23 (pp. 245-250). ACM.}}


		\item {\href{https://www.researchgate.net/profile/Mdsaimul_Islam/publication/283070817_PCA_versus_ICA_in_Visualization_of_Clusters/links/56288c9108aef25a243cfedb.pdf} {Islam MS, \textbf{Islam MS}, Nasser M. \textbf{\textit{"Principal Component Analysis versus Independent Component Analysis in Visualization of Clusters."}} In International Conference on Statistical Data Mining for Bioinformatics Health Agriculture and Environment 2012 Sep 30 (pp. 21-24).}}

		\item {Rajib Chowdhury, Vashkar Chowdhury,\textbf{Sahidul Islam},  Shyla Faria, Saiful Islam, Narayan Prosad Maheswary, Shireen Akhter, Aditya Prasad Dash, Axel Kroeger, Qamar Banu  \textbf{\textit{"Water Depth and Color Choice in Chikungunya Vectors in Bangladesh"}}. \textit{World Health Organization, Dengue Bulletin}}	


		\item {\textbf{Md.  Sahidul Islam}, Md. Saimul Islam, Thomas Hahn  \textbf{\textit{"Prevalence \& Factor Associated with Stunting and Severe Stunting among under Fives in Bangladesh: evidence from 2014 Bangladesh Demographic and Health Survey"}}. (Submitted to Plos One)}	

		\item {Rajib Chowdhury, Vashkar Chowdhury,\textbf{Sahidul Islam},  Shyla Faria, Saiful Islam, Narayan Prosad Maheswary, Shireen Akhter, Aditya Prasad Dash, Axel Kroeger, Qamar Banu.  \textbf{\textit{"Knowledge, Attitude and Practice related to Visceral Leishmaniasis"}}. [Submitted to \textit{Plos NTD}]}	
\end{enumerate}
\end{cvparagraph}

