%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Conference Talks [Selected]}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

\begin{enumerate}[label={[\arabic*]}]
\item {Mohammad Wahiduzzaman, Sharmin Hossain, \textbf{Md. Sahidul Islam}, Andres Lechner, Liaquat Ali. \textit {\textbf {"Clinical Outcome and Its Association with Adherence to Medical Advice among T2DM Subject Attending OPD: Experience from a Tertiary Care Hospital of Bangladesh"}} 8th regional public health conference, Bangladesh University of Health Science, 29-30 December 2017}
		
\item {\href{http://www.dusdaa.org/} {\textbf{ Md. Sahidul Islam}, Md. Saimul Islam, Thomas Hahn, and Mohammed Nasser. \textit {\textbf {"Breast Cancer DNA Microarray Gene Expression Data Analysis using ICA."}} The 2nd International Conference on Statistics for Population and Development, organized by Dhaka University Statistics Department Alumni Association (DUSDAA), 27-29 December, 2015}}
		
\item {\href{http://sites.isrt.ac.bd/icas2014/home}{\textbf {Md. Sahidul Islam}, Mohammed Ali, Md. Saimul Islam, Md. Binyamin, and Mohammed Nasser. \textit {\textbf{"A Comparative Study between ICA, PCA and Their Robust Versions in Visualization of Clusters".}} An Proceedings of the International Conference on Applied Statistics in University of Dhaka, Bangladesh (ICAS'14), 27-29 December, 2014}}
		
\item {\href{http://sites.isrt.ac.bd/icas2014/home} {Md. Bipul Hossen, Md. Binyamin, Md. Ali, Md. Saimul Islam, \textbf {Md. Sahidul Islam}, Md. Nasser, Md. Aminul Haque, Mashahiro Sugimoto. \textbf{\textit {"Performance Evaluation of Several Hierarchical Clustering Algorithms with Proximity Measures".}} In Proceedings of the International Conference on "Statistics in planning and development: Bangladesh perspective", organized by Statistical Association Dhaka, Bangladesh)}}
	
%		\cvitem{Dec 2012}
%		{\href{https://www.researchgate.net/profile/Mdsaimul_Islam/publication/283070817_PCA_versus_ICA_in_Visualization_of_Clusters/links/56288c9108aef25a243cfedb.pdf} {Md. Saimul Islam, \textbf{Md. Sahidul Islam}, and Mohammed Nasser.\textbf{\textit {"PCA vs ICA in Visualization of Clusters",}} In Proceedings of the International Conference on Statistical Data Mining for Bioinformatics Health Agriculture and Environment, ISBN: 978-984-33-5876-9, organize by department of Statistics, University Rajshahi, Bangladesh 21-24 December, 2012}}
\end{enumerate}

\end{cvparagraph}
