%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{http://www.searo.who.int/bangladesh/en/}{World Health Organization, Bangladesh}} % Job title
    {\href{https://www.dropbox.com/sh/bg88dnmjpcicdmn/AACdPh__4UdzmbZgx1FtOz3sa?dl=0}{\textbf {\textit {Vaccine \& Logistic Management Assistant}}}} % Organization
    {Dhaka, Bangladesh} % Location
    {Feb. 2019 --cont.} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Collate and analyze data related to vaccines and logistics to strengthen routine and supplementary immunization services}
	\item {Inventory/stock management with proper record keeping including planning, indenting and distribution of vaccine and logistics by way of coordinating with procurement and supply division, EPI, DGHS; }
	\item {Management of vaccines, syringes, injection safety materials and other relevant logistics at the national level, including estimation of requirements, preparing indents, preparing schedules of deliveries and ensuring timely supply}
	\item {Undertake field visits to support quality distribution of vaccines and logistics and conduct ‘on the job’ trainings;}
	\item {Minimizing vaccine and injection stock-outs and reducing wastages; }
	\item {Assist for evaluating vaccine and logistics requirement for supplementary immunization activities and any new vaccines introduction; }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {\href{http://www.icddrb.org/}{International Centre for Diarrhoeal Disease Research, Bangladesh (icddr,b)}} % Job title
   {\href{https://www.dropbox.com/sh/bg88dnmjpcicdmn/AACdPh__4UdzmbZgx1FtOz3sa?dl=0}{\textbf {\textit {Statistical Officer}}}} 
    {Dhaka, Bangladesh} % Location
    {Aug. 2018 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item{Designing ways of collecting survey data, writhing program for cleaning, preparing and analysing the data.} 
	\item{Prepared statistical modeling and reporting and draw conclusion from the data.}
	\item{Interpreting statistical analysis for policy development, evaluation\& monitoring, forecasting, national statistics and dealing with queries for a range of clients.}
	\item{Developing statistical tools for data preparation and analysis.}
	\item{Develop automated reporting system using R markdown}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{http://www.icddrb.org/}{International Centre for Diarrhoeal Disease Research, Bangladesh (icddr,b)}} % Job title
   {\href{https://www.dropbox.com/sh/bg88dnmjpcicdmn/AACdPh__4UdzmbZgx1FtOz3sa?dl=0}{\textbf {\textit {Monitoirng and Evaluation Officer}}}} 
    {Dhaka, Bangladesh} % Location
    {Sep. 2017 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item{Developed Monitoring \& Evaluation guideline according to project goal for National Kala-azar Elimination Programme (NKEP).}
	\item{Implement the project monitoring \& evaluation strategy and recommendation any possible changes based on data analysis by collecting sample from field on a periodic basis.} 
	\item{Present findings at quarterly board meeting, making recommendations for improvements and acting as an M\&E consultant to executives.} 
	\item{Statistical modeling, data analysis and reports making in a monthly, quarterly, half yearly, and present the findings in board meeting.}
	\item{Review the performance indicators and reports to the different stakeholders to suggest necessary changes and current status for program success.}
	\item{Provide statistical support example, sample size calculation, sampling techniques, statistical modeling, data analysis to other projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{http://www.kantar.com/}{KANTAR MRB}} % Job title
   {\href{https://www.dropbox.com/sh/bg88dnmjpcicdmn/AACdPh__4UdzmbZgx1FtOz3sa?dl=0}{\textbf {\textit {Research Manager}}}} % Organization
    {Dhaka, Bangaldesh} % Location
    {Aug. 2014 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item{Research and transform information from raw data into an easily understood analysis that identifies pattern, trend and insights for the program.}
	\item{Proposal writing \& submission, questionnaire development, research designing, sampling preparation, statistical modeling and data analysis.}
	\item{Ensured accurate and consistent statistical analysis by meticulously going through the data validating results.}
	\item{Preparing presentation and delivering the projects output to clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{http://www.kantar.com/}{KANTAR MRB}} % Job title
   {\href{https://www.dropbox.com/sh/bg88dnmjpcicdmn/AACdPh__4UdzmbZgx1FtOz3sa?dl=0}{\textbf {\textit {Analytics Executive}}}} % Organization
    {Dhaka, Bangladesh} % Location
    {Seo. 2014 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item{Successfully completed more than 20 projects including National Mobile Financial Service Survey (NMFSS), National Media Survey (NMS) etc.}
\item{Database preparation, data cleaning, error program writing and checking inconsistent data.}
\item{Convert data into actionable insights by predicting and modeling future outcomes.}
\item{CAPI (Computer Assist Personal Interview) and CATI (Computer Assist Telephonic Interview) and mobile base questionnaire development.}
\item{Designed and built statistical analysis models on large datasets.}
\item {Create visually impactful dashboards in Excel and Tableau for data reporting by using pivot tables and VLOOKUP. Extracted, interpreted and analyzed data to identify key metrics and transform raw data into meaningful, actionable information.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
