%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
      \begin{itemize}[noitemsep,leftmargin=0.3cm]  % Description(s) of tasks/responsibilities
  	 \setlength{\itemsep}{0pt}
    	\setlength{\parskip}{0pt}
    	\setlength{\parsep}{0pt}   


	\item Comprehensive advance knowledge of R Programming, IBM SPSS, Stata, MS Word, Excel, PowerPoint.
	\item Ability to work well with numbers and analyze complex data.
\item Following ’best practice’ in research design and documentation.
\item In-depth knowledge of research tools and databases.
\item Ability to work in a structured and organised manner.
\item Experience of quantitative and qualitative research.
\item Confidently communicate market research insights to influence business decisions.
\item Expert-level understanding of performance evaluation, including the assessment of metrics, comparative analysis, and future projections based off of improvement.
\item Familiar with data mining applications used to retrieve information for analysis, as well as electronic reporting tools.
\item Excellent oral and written communication skills, evidenced by comfort in sharing and interpreting report data with managers and
preparing statements to be reviewed by stakeholders.
\item Organized and detailed in all aspects of work.
\end{itemize}
\end{cvparagraph}
