
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{lipsum}
\usepackage{fontawesome}
\usepackage{blindtext}
\usepackage{scrextend}
% Configure page margins with geometry
\geometry{left=1.8cm, top=1.5cm, right=1.8cm, bottom=1cm, footskip=.5cm}


\definecolor{mycolor}{RGB}{241,254,249}
\pagecolor{mycolor}
% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile.jpg}
\name{Md. Sahidul}{Islam}
\position{Monitoring and Evaluation Officer{\enskip\cdotp\enskip}Statistician{\enskip\cdotp\enskip}Researcher {\enskip\cdotp\enskip} Data Analyst}
\address{House no. 169/A, Santiniketon, Niketon Bazar, Tejgaon Industrial Area, Dhaka-1208}

\mobile{(+88) 01737-272 633}
\email{ripon.ru.statistics@gmail.com}
%\homepage{www.posquit0.com}
%\github{ripon08054718}
\linkedin{sahidul-islam-ripon-ab543342/}
% \gitlab{gitlab-id}
%\stackoverflow{@ripon_ru}{Md. Sahidul Islam}
%\twitter{ripon\_ru}
 \skype{ripon.ru}
% \reddit{reddit-id}
% \extrainfo{extra informations}

\quote{``Be the change that you want to see in the world."\vspace{-1cm}}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {}
  {To,\\Country Manager, \\British Red Cross, \\684-686, Bara Mogh Bazar, Dhaka-1217, Bangladesh \vspace{-1cm}}
% The date on the letter, default is the date of compilation
\letterdate{\today}

% The title of the letter
\lettertitle{\vspace{-3cm} Subject: Job Application for the post of ``Planning, Monitoring, Evaluation, Accountability and Learning (PMEAL) Officer"}
% How the letter is opened
\letteropening{}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Md. Sahidul Islam~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

Dear Sir,

Upon discovering your posting for a new ``Planning, Monitoring, Evaluation, Accountability and Learning (PMEAL) Officer", I felt compelled to submit my resume for your review. As an experienced in public health research,  project monitoring \& evaluation and reporting with additional expertise knowledge in data analysis with a solid background in statistics and having a strong technical aptitude, I am prepared to significantly contribute to your organization in that roles.

I have completed both Bachelor and Masters degree in Statistics from University of Rajshahi, Bangladesh. Moreover, I have more than 7 conference papers, four peer reviewed journal publications, and a master’s dissertation. I achieved certifications of ``R programming", ``Data Scientist's Toolbox", ``Computing for Data Analysis" course with distinction from Johns Hopkins University, Bloomberg School of Public Health.

I am presently working as a ``MIS Officer"  at Shushilan, Bangladesh.  Before that I served 1 year as ``Monitoring and Evaluation Officer" in icddrb (www.icddrb.org), and 8 months as a ``Research Manager" with 2 years 3 months as ``Analytics Executive" at KANTAR MRB (www.kantar.com). I have advance knowledge of handling various data analysis tools: R programming, IBM SPSS, Excel,  Stata, Matlab, Maple, Minitab, AMOS, Weka, Eviews, Rattle etc. Also I am experienced in Geospatial data analysis, vector and raster mapping with knowledge of ArcGIS/QGIS.

I have vast experience on various projects including National Kala-azar Elimination Programme, Effectiveness of Oral Cholera Vaccine, Maternal and Child Health and Nurtrition, National Media Survey, Mobile Financial Services, Local Stability Initiatives, Good Governance and Capacity Building Programmes for various donors including USAID, DFID, InterMedia, CDC, Gallup, CIDA and various government and private funders. I have developed, managed and implemented databases to track the flow of information within complex, multi-layered, geographically dispersed projects, placing a specific emphasis on data quality.



%The following are my most relevant qualifications and accomplishments.\\
%\begin{itemize}
%	\item {Developed Monitoring and Evaluation guideline according to project goal.}
%	\item {International migration: a global issue sciences po.}
%	\item Implement the project monitoring \& evaluation strategy and recommendation any possible changes based on data analysis by collecting sample from field on a periodic basis. 
%	\item Developing KPIs to see a clearer picture to SEP management and staff whether the implementation process is moving in the right direction towards achieving its overall goal and specific objectives.
%	\item Measuring the achievement of the indicators, present findings at quarterly board meeting, making recommendations for improvements. 
%	\item Statistical modeling, data analysis and reports making in a monthly, quarterly, half yearly, and present the findings in board meeting. 
%	\item Review the performance indicators and reports to the different stakeholders to suggest necessary changes and current status for program success. 
%	\item Provide statistical support example, sample size calculation, sampling techniques, statistical modeling, data analysis to other projects.
%\end{itemize} 
On a personal level, I am detail-oriented, organized, and precise in my work. I have strong communication skills with a knack for clear and illuminating presentation. I’m comfortable on my own facing the numbers, but I really enjoy being part of a motivated team of smart people. I believe that my proven skills and experience in research, project monitoring and evaluation, vector and raster mapping, environmental fundraising and strategic communication to various audiences make me an excellent candidate for the PMEAL position.\\\\
Please find my contact information at the top of this letter, as well as on my enclosed resume. I appreciate your time spent reading this letter, and look forward to connecting in the future.


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
